The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-07-26 albatros_paper.tex
HCC updated numbers for fine-res baseband spectra

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_auto_compare.jpg}
    \caption{\attention{Placeholder figure} Autospectra for one
      polarization from an \albatros\ pathfinder at MARS (see text for
      details).  The top row shows spectra that are accumulated
      directly by the SNAP board, and the middle row shows spectra
      computed from baseband data with 4-bit quantization.  The two
      frequency windows, 5.3--12.6~MHz and 12.6--20.0~MHz, are
      recorded at two separate times, and all waterfall plots are
      shown with 61-kHz resolution.  The bottom row compares the mean
      autospectra, with finer, \attention{numbers here} resolution of
      the baseband spectra.}
    \label{Fig:baseband_direct_auto}
  \end{center}
\end{figure}

@@

\autoref{Fig:baseband_direct_auto} shows autospectra for one
polarization of the \albatros\ pathfinder installed at MARS, comparing
the accumulated spectra that are directly computed by the SNAP board
against spectra that are calculated from baseband data with 4-bit
quantization.  (Autospectrum information is not preserved with 1-bit
quantization.)  Baseband data were recorded over two frequency
windows, 5.3--12.6~MHz and 12.6--20.0~MHz, at separate times, and the
corresponding accumulated spectra from the SNAP board are shown for
the same frequency and time ranges.  All of the waterfall plots have
the same 61-kHz frequency resolution, set by the resolution of the
spectra computed by the SNAP board.  The overplotted mean spectra are
shown with finer resolution (\attention{numbers go here}) from the
baseband data to illustrate the additional information that is not
available in the accumulated spectra.  For these mean spectrum plots,
the baseband data are processed by
inverting\footnote{\url{https://github.com/jrs65/pfb-inverse}} the
polyphase filter bank to recover time-domain data, and the
forward-direction polyphase filter bank is then applied to
concatenated timestreams of an appropriate total length to set the
desired frequency resolution.  \autoref{Fig:baseband_direct_phase}
shows waterfall plots of phases computed from the cross-correlation
between the two orthogonal polarizations of the \albatros\ pathfinder
at MARS, comparing the directly accumulated and baseband data.  For
both the autospectra and phases, the baseband data qualitatively agree
with the data directly accumulated by the SNAP board, up to small
differences caused by the 4-bit quantization.

>>>>

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_auto_compare.jpg}
    \caption{\attention{Placeholder figure} Autospectra for one
      polarization from an \albatros\ pathfinder at MARS (see text for
      details).  The top row shows spectra that are accumulated
      directly by the SNAP board, and the middle row shows spectra
      computed from baseband data with 4-bit quantization.  The two
      frequency windows, 5.3--12.6~MHz and 12.6--20.0~MHz, are
      recorded at two separate times, and all waterfall plots are
      shown with 61-kHz resolution.  The bottom row compares the mean
      autospectra, with finer, 14.6-kHz resolution of
      the baseband spectra.}
    \label{Fig:baseband_direct_auto}
  \end{center}
\end{figure}

@@

\autoref{Fig:baseband_direct_auto} shows autospectra for one
polarization of the \albatros\ pathfinder installed at MARS, comparing
the accumulated spectra that are directly computed by the SNAP board
against spectra that are calculated from baseband data with 4-bit
quantization.  (Autospectrum information is not preserved with 1-bit
quantization.)  Baseband data were recorded over two frequency
windows, 5.3--12.6~MHz and 12.6--20.0~MHz, at separate times, and the
corresponding accumulated spectra from the SNAP board are shown for
the same frequency and time ranges.  All of the waterfall plots have
the same 61-kHz frequency resolution, set by the resolution of the
spectra computed by the SNAP board.  In the overplotted mean spectra,
the baseband data are shown with finer, 14.6-kHz resolution to
illustrate the additional information that is not available in the
accumulated spectra.  For these mean spectrum plots, the baseband data
are processed by
inverting\footnote{\url{https://github.com/jrs65/pfb-inverse}} the
polyphase filter bank to recover time-domain data, and the
forward-direction polyphase filter bank is then applied to
concatenated timestreams of an appropriate total length to set the
desired frequency resolution.  \autoref{Fig:baseband_direct_phase}
shows waterfall plots of phases computed from the cross-correlation
between the two orthogonal polarizations of the \albatros\ pathfinder
at MARS, comparing the directly accumulated and baseband data.  For
both the autospectra and phases, the baseband data qualitatively agree
with the data directly accumulated by the SNAP board, up to small
differences caused by the 4-bit quantization.
